### 2022-01-03 sections/papers.tex
Update papers.tex

\item{\small Gonz\'alez-Bustamante, B. (2013). Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010). {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436cl}}} \vspace{1mm}

%% \item{\small Gonz\'alez-Bustamante, B. (2013). Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010). {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}

>>>>

\item{\small Gonz\'alez-Bustamante, B. (2013). Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010). {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119--153. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{https://doi.org/10.5354/0716-1077.2013.27436}{\textcolor{blue}{10.5354/0716-1077.2013.27436cl}}. {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
